### 2011-09-09 NYAS_abstract/abstract.tex
Final NYAS abstract

Our work operates within the framework of topic modeling. Our approach learns
topic models of the underlying data and labeling strategies in a joint model,
while leveraging the hierarchical structure of the labels. For the sake of
simplicity, we focus on is-a hierarchies, but the model can be
applied to other structured label spaces. Our work extends supervised latent Dirichlet
allocation (sLDA)~\cite{BleiMcAuliffe2008} to take advantage of hierarchical
supervision and proposes an efficient way to incorporate such information into the model. 
We hypothesize that the context of labels within
the hierarchy provides valuable information about labeling. Other models, such as LabeledLDA\citep{Ramage2009}, incorporate LDA and supervision; However, none of these models leverage dependency structure in the label space.

@@

HSLDA is a model for hierarchically, multiply-labeled, bag-of-word data.  We
will refer to individual groups of bag-of-word data as documents.  Let $w_{n,d}
\in \Sigma$ be the $n$th observation in the $d$th document.  Let $\mathbf{w}_d
= \{w_{1,d},\ldots,w_{1,N_d}\}$ be the  set of $N_d$ observations in document
$d$.  Let there be $D$ such documents and let the size of the vocabulary be
$V=|\Sigma|$.  Let the set of labels be $\mathcal{L}=\left\{
  l_{1},l_{2},\ldots,l_{\left|\mathcal{L}\right|}\right\} $. Each label labels
$l \in \mathcal{L}$, except root, has a parent $\mathrm{pa}(l) \in \mathcal{L}$
also in the set of labels. 
 We will for exposition purposes assume that this label set has hard ``is-a''
 parent-child constraints (explained later), although this assumption can be
 relaxed at the cost of more computationally complex inference.  Such a label hierarchy forms a multiply rooted tree.  Without loss of generality we will consider a tree with a single root $r\in\mathcal{L}$.  Each document has a variable $y_{l,d} \in \{-1,1\}$ for every label which indicates whether the label is applied to document $d$ or not.   In most cases $y_{i,d}$ will be unobserved, in some cases we will be able to fix its value because of  constraints on the label hierarchy, and in the relatively minor remainder its value will be observed.  In the applications we consider, only positive label applications are observed.

%In HSLDA, the bag-of-word document data is modeled using the LDA
%mixed-membership mixture model with global topic estimation.
In HSLDA, documents are modeled using the LDA mixed-membership mixture model
with global topic estimation. Label responses are generated using a conditional
hierarchy of probit regressors\cite{gelmanbda04}. The HSLDA graphical model is given in
Figure~\ref{fig:graphical_model}. In the model, $K$ is the number of LDA
``topics'' (distributions over the elements of $\Sigma$), $\boldsymbol\phi_k$
is a distribution over ``words,'' $\boldsymbol\theta_d$ is a document-specific
distribution over topics, $\boldsymbol\beta$ is a global distribution over
topics, Dir$_{K}(\cdot)$ is a $K$-dimensional Dirichlet distribution,
$\mathcal{N}_{K}(\cdot)$ is the $K$-dimensional Normal distribution,
$\mathbf{I}_{K}$ is the $K$ dimensional identity matrix,  $\mathbf{1}_d$ is the
$d$-dimensional vector of all ones, and $\mathbb{I}(\cdot)$ is an indicator
function that takes the value $1$ if its argument is true and $0$ otherwise.

>>>>

Our work operates within the framework of topic modeling. Our approach learns
topic models of the underlying data and labeling strategies in a joint model,
while leveraging the hierarchical structure of the labels. For the sake of
simplicity, we focus on is-a hierarchies, but the model can be
applied to other structured label spaces. Our work extends supervised latent Dirichlet
allocation (sLDA)~\cite{BleiMcAuliffe2008} to take advantage of hierarchical
supervision and proposes an efficient way to incorporate such information into the model. 
We hypothesize that the context of labels within
the hierarchy provides valuable information about labeling. Other models, such as LabeledLDA~\citep{Ramage2009}, incorporate LDA and supervision; however, none of these models leverage dependency structure in the label space.

@@

HSLDA is a model for hierarchically, multiply-labeled, bag-of-word data.  We
will refer to individual groups of bag-of-word data as documents.  Let $w_{n,d}
\in \Sigma$ be the $n$th observation in the $d$th document.  Let $\mathbf{w}_d
= \{w_{1,d},\ldots,w_{1,N_d}\}$ be the  set of $N_d$ observations in document
$d$.  Let there be $D$ such documents and let the size of the vocabulary be
$V=|\Sigma|$.  Let the set of labels be $\mathcal{L}=\left\{
  l_{1},l_{2},\ldots,l_{\left|\mathcal{L}\right|}\right\} $. Each label
$l \in \mathcal{L}$, except root, has a parent $\mathrm{pa}(l) \in \mathcal{L}$
also in the set of labels. 
 We will for exposition purposes assume that this label set has hard ``is-a''
 parent-child constraints, although this assumption can be
 relaxed at the cost of more computationally complex inference.  Such a label hierarchy forms a multiply rooted tree.  Without loss of generality we will consider a tree with a single root $r\in\mathcal{L}$.  Each document has a variable $y_{l,d} \in \{-1,1\}$ for every label which indicates whether the label is applied to document $d$ or not.   In most cases $y_{i,d}$ will be unobserved, in some cases we will be able to fix its value because of  constraints on the label hierarchy, and in the relatively minor remainder its value will be observed.  In the applications we consider, only positive label applications are observed.

%In HSLDA, the bag-of-word document data is modeled using the LDA
%mixed-membership mixture model with global topic estimation.
In HSLDA, documents are modeled using the LDA mixed-membership mixture model
with global topic estimation. Label responses are generated using a conditional
hierarchy of probit regressors\cite{gelmanbda04}. The HSLDA graphical model is given in
Figure~\ref{fig:graphical_model}. In the model, $K$ is the number of LDA
``topics'' (distributions over the elements of $\Sigma$), $\boldsymbol\phi_k$
is a distribution over ``words,'' $\boldsymbol\theta_d$ is a document-specific
distribution over topics, and $\boldsymbol\beta$ is a global distribution over
topics.
%% , Dir$_{K}(\cdot)$ is a $K$-dimensional Dirichlet distribution,
%% $\mathcal{N}_{K}(\cdot)$ is the $K$-dimensional Normal distribution,
%% $\mathbf{I}_{K}$ is the $K$ dimensional identity matrix,  $\mathbf{1}_d$ is the
%% $d$-dimensional vector of all ones, and $\mathbb{I}(\cdot)$ is an indicator
%% function that takes the value $1$ if its argument is true and $0$ otherwise.
